Generalized multidimensional parameters of the MCLM

### 2024-02-15 output/Transcription_Mario_Luzardo/Transcription_of_Marios_derivations.Rmd

```{r includes, cache=FALSE}
source("R/Formulas.R")
source("R/Graphical_example_transcriptions_Mario.R")
source("R/Output.R")
```

>>>>

```{r includes, cache=FALSE}
source("R/Formulas.R", encoding = 'UTF-8')
source("R/Graphical_example_transcriptions_Mario.R", encoding = 'UTF-8')
source("R/Output.R", encoding = 'UTF-8')
```
